\Large Classifying Vehicles From Automatic Number \\ Plate Recognition Camera Scans

### 2018-01-30 intro.tex
Moved text to dataset.tex

@@

\section{Tyne and Wear ANPR Data}
\label{s.ncl}
Automatic number plate recognition (ANPR) cameras are actively employed in urban traffic environments and play an important role in day-to-day intelligent transportation systems. They can be used by Urban Traffic Control and Management (UTMC) entities; by comissioned highway agencies in electronic toll collection; or by law enforcement organisations in the detection of speeding vehicles and validation of number plate registrations. The wide diversity of applications, paired with the large improvements in price-to-performance ratios of ANPR hardware and software systems, has resulted in the increase of installed ANPR cameras across the UK~\cite{EvolutionUTMC2013, SurveyITS2011}.

In the area of Tyne and Wear, United Kingdom, there are over 250 active ANPR cameras. Scans made by these cameras are stored in a central database by the UTMC of Tyne and Wear and then used to compute travel times across particular links of interest in the road network. These are usually major roads that see high volumes of traffic, or road segments more prone to traffic jams. Average journey times can then be conveyed back to the drivers by the way of Variable Message Signs (VMS) or web based applications. ANPR cameras provide additional trip information, besides simple link counts, that has

 estimating travel demands and traffic states. extended traditional methods of  travel demands

>>>>

%Therefore, number plate scans provide additional trip information, besides simple link counts, that has

 %estimating travel demands and traffic states. extended traditional methods of  travel demands

@@
